Approximation as Differentiation

### 2025-04-02 notes/sec/cmon-enriched.tex
WIP.

\subsubsection{$\CMon$-enriched presheaf}

For any monoidal category $\mathscr{V}$ and $V$-enriched categories $C$ and $D$, the action of a
\emph{$\mathscr{V}$-enriched} functor $F: C \to D$ on morphisms takes the form of a morphism $F_{X,Y}:
\Hom{C}{X}{Y} \to \Hom{D}{F(X)}{F(Y)}$ between hom-objects in $\mathscr{V}$ that is
\emph{$\mathscr{V}$-natural}, i.e.~makes the following diagram commute:

\begin{center}
\begin{tikzcd}
   \Hom{C}{Y}{Z} \tensor \Hom{C}{X}{Y} \arrow[r, "- \comp -"] \arrow[d, "F_{Y,Z} \tensor F_{X,Y}"'] & \Hom{C}{X}{Z} \arrow[d, "F_{X,Z}"] \\
   \Hom{D}{F(Y)}{F(Z)} \tensor \Hom{D}{F(X)}{F(Y)} \arrow[r, "- \comp -"'] & \Hom{D}{F(X)}{F(Z)}
\end{tikzcd}
\end{center}

Write $\Func{C}{D}_{\mathscr{V}}$ for the category of $\mathscr{V}$-enriched functors from $C$ to $D$. In the
specific setting of a $\CMon$-enriched presheaf $F: C^\op \to \CMon$, this means that $F$ preserves the
additive structure of morphisms:
\begin{itemize}
\item $F(0_{X,Y}) = 0_{F(Y),F(X)}$
\item $F(f + g) = F(f) + F(g)$
\end{itemize}
It then follows automatically that $F$ also preserves bilinear composition, i.e.:
\begin{itemize}
\item $F(f) \comp F(0) = F(f) = F(0) \comp F(f)$
\item $F(f + g) \comp F(h) = F(h \comp f) + F(h \comp g)$
\item $F(h) \comp F(f + g) = F(f \comp h) + F(g \comp h)$
\end{itemize}
in addition to the usual functorial properties.

@@

\noindent For a $\mathscr{V}$-enriched category $C$, the hom-functor $\Hom{C}{-}{X}: C \to \mathscr{V}$ sends
objects $Y$ in $C$ to hom-objects $\Hom{C}{Y}{X}$ in $\mathscr{V}$ and morphisms $f: Y \to Z$ in $C$ to
morphisms

>>>>

\subsubsection{$\CMon$-enriched presheaves}

\begin{definition}[$\mathscr{V}$-enriched functor]
For any monoidal category $(\mathscr{V}, \tensor, I)$ and $V$-enriched categories $C$ and $D$, a
\emph{$\mathscr{V}$-enriched} functor $F: C \to D$ on morphisms is a family of morphisms $F_{X,Y}:
\Hom{C}{X}{Y} \to \Hom{D}{F(X)}{F(Y)}$ between hom-objects in $\mathscr{V}$ that makes the following diagrams
in $\mathscr{V}$ commute:

\begin{center}
\begin{tikzcd}[column sep=1.8cm]
I \arrow[d, equals] \arrow[r, "\id_X"] & \Hom{C}{X}{X} \arrow[d, "F_{X,X}"] \\
I \arrow[r, "\id_{F(X)}"'] & \Hom{D}{F(X)}{F(X)}
\end{tikzcd}
\hspace{5mm}
\begin{tikzcd}[column sep=2.6cm]
   \Hom{C}{Y}{Z} \tensor \Hom{C}{X}{Y} \arrow[r, "\comp_{X,Y,Z}"] \arrow[d, "F_{Y,Z} \tensor F_{X,Y}"'] & \Hom{C}{X}{Z} \arrow[d, "F_{X,Z}"] \\
   \Hom{D}{F(Y)}{F(Z)} \tensor \Hom{D}{F(X)}{F(Y)} \arrow[r, "\comp_{F(X),F(Y),F(Z)}"'] & \Hom{D}{F(X)}{F(Z)}
\end{tikzcd}
\end{center}
\end{definition}

Write $\Func{C}{D}_{\mathscr{V}}$ for the category of $\mathscr{V}$-enriched functors from $C$ to $D$.

In the specific setting of a $\CMon$-enriched presheaf $F: C^\op \to \CMon$, this means that $F$ preserves the
additive structure of morphisms:
\begin{itemize}
\item $F(0_{X,Y}) = 0_{F(Y),F(X)}$
\item $F(f + g) = F(f) + F(g)$
\end{itemize}
It then follows automatically that $F$ also preserves bilinear composition, i.e.:
\begin{itemize}
\item $F(f) \comp F(0) = F(f) = F(0) \comp F(f)$
\item $F(f + g) \comp F(h) = F(h \comp f) + F(h \comp g)$
\item $F(h) \comp F(f + g) = F(f \comp h) + F(g \comp h)$
\end{itemize}
in addition to the usual functorial properties.

@@

\noindent For a $\mathscr{V}$-enriched category $C$, the hom-functor $\Hom{C}{-}{X}: C \to \mathscr{V}$ is
$\mathscr{V}$-enriched.
